---
title: "Probabilistic Selection Task and Dietary Restraint Analysis"
author: "JRS"
date: "7/31/2019"
output: html_document
---
## About this analysis 
This containst the behavioral data analysis for Sadler, Acosta, Shearrer, and Burger (2019) DRES paper. File has been adapted to use deidentified data. This script will reproduce plots and results 

```{r, echo=FALSE}
library(readxl)
library(ggplot2)
library(psych)
library(table1)
#import data file
df1 <- read.csv("/Users/jennygilbert/Documents/bevel_DRES_analysis/data/deid_bevel.csv")
```

##Select Restraint Groups
1. Find cutoffs for tertiles
```{r}
quantile(df1$DRES, c(.33, .66)) 
```
2. Create DREScat variable with DRES categories 
```{r}
attach(df1)
df1$DREScat[DRES > 2.5] <- "high_restraint"
df1$DREScat[DRES > 1.837 & DRES <= 2.5] <- "mid_restraint"
df1$DREScat[DRES <= 1.837] <- "low_restraint"
detach(df1)
print(df1$DREScat)
```
2. Make a new DF with participants in the high restraint and low restraint groups
```{r}
df <- df1[ which(df1$DREScat=='high_restraint' | df1$DREScat =="low_restraint"), ]
print(df$ID)
```

##Generate Table 1: Sample Charateristics
```{r, echo=FALSE}
df$DREScat <- 
  factor(df$DREScat, levels=c('low_restraint','high_restraint'),
         labels=c("Low Dietary Restraint", "High Dietary Restratint"))

df$test_result_group <- 
  factor(df$test_result_group, levels=c('learner','nonlearner','punish_learner','reward_learner'),
         labels=c("Choose Reward and Avoid Punishment", "No Learning", "Avoid Punishment",
                  "Choose Reward"))

df$sweetstim_level <- 
  factor(df$sweetstim_level, levels=c('1','2','3','4'),
         labels=c("14", "21", "28",
                  "35"))

df$bitterstim_level <- 
  factor(df$bitterstim_level, levels=c('1','2','3','4'),
         labels=c("12", "24", "48",
                  "72"))

label(df$sex) <- "Sex"
label(df$BMI) <- "Body Mass Index"
label(df$age) <- "Age"
label(df$DRES) <- "DEBQ: Restratint"
label(df$external_eating) <- "DEBQ: External Eating"
label(df$emotional_eating) <- "DEBQ: Emotional Eating"
label(df$PORTIONS_SSB) <- "Self-Reported Daily SSB Intake"
label(df$TOTAL_KCAL) <- "Self-Reported Daily Intake"
label(df$nback_accuracy) <- "N-Back Accuracy"
label(df$sweetstim_level) <- "Sweetness of Selected Reward"
label(df$sweetstim_pleasent) <- "Plesantness Rating of Selected Reward"
label(df$bitterstim_level) <- "Bitterness of Selected Punishment"
label(df$bitterstim_pleasent) <- "Plesantness Rating of Selected Punishment"
label(df$PSTtraining_._correct) <- "Accuracy during PST Training"
label(df$test_result_group) <- "Reinforcer Sensitivity on PST Behavioral Posttest"

units(df$age) <- "years"
units(df$BMI) <- "kg/m^2"
units(df$TOTAL_KCAL) <- "kcal"
units(df$PORTIONS_SSB) <- "servings"
units(df$sweetstim_level) <- "grams of sugar per 300mL"
units(df$bitterstim_level) <- "mg of quinine per 300mL"

my.render.cont <- function(x) {
    with(stats.apply.rounding(stats.default(x), digits=2), c("",
        "Mean (SD)"=sprintf("%s (&plusmn; %s)", MEAN, SD)))
}
my.render.cat <- function(x) {
    c("", sapply(stats.default(x), function(y) with(y,
        sprintf("%d (%0.0f %%)", FREQ, PCT))))
}
```

Use Table1 package to make participant characteristics table
```{r}
table1(~ BMI  + age + sex + DRES + external_eating + emotional_eating + TOTAL_KCAL + PORTIONS_SSB + nback_accuracy + 
         sweetstim_level + sweetstim_pleasent + bitterstim_level + bitterstim_pleasent + PSTtraining_._correct 
       + test_result_group | DREScat, data=df, render.continuous=my.render.cont, render.categorical=my.render.cat)
```

##Test for between group differences in characteristics 

```{r}
t.test(BMI ~ DREScat, data = df)
t.test(age ~ DREScat, data = df)
chisq.test(df$DREScat, df$sex, correct=FALSE)
t.test(DRES ~ DREScat, data = df)
t.test(external_eating ~ DREScat, data = df)
t.test(emotional_eating ~ DREScat, data = df)
t.test(TOTAL_KCAL ~ DREScat, data = df)
t.test(PORTIONS_SSB ~ DREScat, data = df)
t.test(nback_accuracy ~ DREScat, data = df)
chisq.test(df$sweetstim_level, df$DREScat, correct=FALSE)
t.test(sweetstim_pleasent ~ DREScat, data = df)
chisq.test(df$bitterstim_level, df$DREScat, correct=FALSE)
t.test(bitterstim_pleasent ~ DREScat, data = df)
t.test(PSTtraining_._correct ~ DREScat, data = df)
chisq.test(df$DREScat, df$test_result_group, correct=FALSE)
```

## Generate plots to visualize differneces between groups
```{r}
p <- ggplot(df, aes(x=DREScat, y=BMI)) 
p + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2) + xlab("Dietary Restraint Groups") +
  ylab("Body Mass Index") + theme_bw(base_size = 14) + theme_classic()
```

```{r}
p <- ggplot(df, aes(x=DREScat, y=nback_accuracy)) 
p + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2) + xlab("Dietary Restraint Groups") +
    ylab("N-Back Accuracy") + theme_bw(base_size = 14) + theme_classic()
```

```{r}
DRES_Palette <- c("grey99", "grey60")

tbl_learner <- with(df, table(test_result_group, DREScat))
ggplot(as.data.frame(tbl_learner), aes(factor(test_result_group), Freq, fill = DREScat)) +
  geom_col(position = "dodge", colour="black") + theme_minimal() + scale_fill_manual(values=c(DRES_Palette), name = "Dietary Restraint Groups", labels = c("Low", "High")) +
  labs(y = "Number of Participants", x = "PST Posttest Performance") + ylim(0,13)
```

```{r}
tbl_sweet <- with(df, table(sweetstim_level, DREScat))
ggplot(as.data.frame(tbl_sweet), aes(factor(sweetstim_level), Freq, fill = DREScat)) +
  geom_col(position = "dodge", colour="black") + theme_minimal() + 
  scale_fill_manual(values=c(DRES_Palette), name = "Dietary Restraint Groups", labels = c("Low","High")) + 
  labs(y = "Number of Participants", x = "Sweetness Selected as Reward (g sugar/300mL") 
```

```{r}
tbl_bitter <- with(df, table(bitterstim_level, DREScat))
ggplot(as.data.frame(tbl_bitter), aes(factor(bitterstim_level), Freq, fill = DREScat)) +
  geom_col(position = "dodge", colour="black") + theme_minimal() + 
  scale_fill_manual(values=c(DRES_Palette), name = "Dietary Restraint Groups", labels = c("Low","High")) + 
  labs(y = "Number of Participants", x = "Bitterness Selected as Punishment (ppm quinine)") 
```

